%% This is emulateapj reformatting of the AASTEX sample document
%%
\documentclass[iop]{emulateapj}
\begin{document}

\title{Fate Of Stars at sun's location in the disk of Andromeda}

\author{Rafia Bushra}
\affil{Astronomy Department, University of Arizona}

\begin{abstract}
    A sentence that defines the topic
    2. A sentence that says why the topic is important
    3. A sentence that says what question you are exporing 4. A sentence about why that question is important
    5. A sentence that states what you found
    6. A conclusion about what your finding means.
    The rest of the report should expand on each of the above bullet points in the abstract. Follow the below guidelines.
\end{abstract}

\section{Introduction}

    Define the topic you are studying and state why it matters. Overview our current understanding of the topic.
    What are the open questions?
    Cite at least 3 journal papers.

\section{This Project}

    State what question(s) you are exploring
    Why is each question interesting/important? Relate back to intro.


\section{Methods}

    Write a paragraph that describes the simulation you are using. Details can be found in: van der Marel, Besla +2012 ApJ 753
    Describe the code you wrote. What equations did you use? At least one component of the code must be unique to you (you can’t only use code from homework and in class labs - but you can use the solutions as a starting point to create your code).
    
\section{Results}
    
    1. Include at least two plots (with proper labels and figure captions). 
    2. Describe what your code returned. What did you find? Describe what is in the plot.

\section{Discussion}

    What did you learn? What do your results mean? What is the importance of your results ?

\section{Conclusion}

    1. Summarize your report - i.e expand a bit on each line of the abstract.
    2. Comment on future directions - what other things could you do to explore the topic further?

\begin{thebibliography}{}

    \bibitem[Auri\`ere(1982)]{aur82} Auri\`ere, M.  1982, \aap,
        109, 301
    
\end{thebibliography}

\clearpage

\end{document}

